\documentclass[a4paper]{article}

\usepackage[latin1]{inputenc}
\usepackage[english]{babel}

\usepackage{qtree}

%\newcommand{\phrase}[1]{\textit{#1}}

\setlength{\hoffset}{-.5in}


\begin{document}
\title{The annotation system of HunMorph}

\maketitle

\section{Introduction}

The annotation system for Hungarian morphology was designed to satisfy at
least three, sometimes contradictory, conditions. The annotation has to be

\begin{itemize}
\item informative: it has to reflect the morphological information of a
given word-form,

\item adequate: it should use linguistically adequate categories, and

\item simple: easily processable by machines and humans as well.

\end{itemize}

These conditions are difficult to fulfill simultaneously. Being simple is
opposed to both being adequate and informative, on the other hand the
conditions mostly depend on the users' aim, whether they use the
annotation system for spell-checking, stemming, syntactic analysis or
statistical research. 

\section{Representing inflectional information as trees}
%\section{Inflexiók}

The morphological description of a word has to include every inflectional
feature of a given word-form. Most inflectional features play a
role in syntactic analysis. Such morphosyntactic features are usually
represented in an attribute-value-structure (AVS) \cite{tron2002}. An AVS
is independent of both the the surface form of the word and the formal
features of the morphosyntactic properties.

In attempting to align the above conditions we chose not to make a decision in
the question of morphological segmentation. Whether we treat a morph as a
whole or segment it into as many parts as the number of the morphemes it
represents is a question of the chosen morphological framework. E.g. the
morph '\textit{-jaim}', though corresponds to more than one morphological
property (1st person, singular possessor and plural possessed), these
properties cannot be unambiguously associated with separate parts of the
morph. Therefore, our annotation system does not employ the notion of
segmentation in the case of suffixes. This way the annotation
could be both theory neutral and modular, furthermore, it remains independent
of the surface form of the word.

The morphological features of a word-form have two important properties
with regard to the annotation system. The features are 
\begin{itemize}
\item hierarchical, i.e. certain features require the presence of other
features,

\item asymmetrical, i.e. certain values of a feature are considered marked,
while others unmarked. 
\end{itemize}

These properties are best expressed by labelled trees. The roots of the
trees represent the equivalence classes of lexical entries with regard to
inflection (these correspond to part-of-speech categories) and the
vertices are the inflectional features. The vertices in the graph define a
path with the positive values of the features. This means that the graph
is capable of encoding a binary attribute-value-structure where a vertex
can have a daughter only if it has positive value
\cite{kornai1989}\footnote{This is a
special interpretation of markedness.}. The labelled tree satisfies all three
conditions. It is

\begin{itemize}
\item informative, as it represents morphological information in an AVS,

\item adequate, as it captures morphological markedness and the
hierarchical nature of inflectional information, and

\item simple, as it can be automatically transformed into an AVS,
furthermore, it can easily be linearized.

\end{itemize}


\section{POS categories of HunMorph}

The valid POS categories ar listed in Table \ref{pos_list}. Inflectable
categories are: ADJ, NOUN, NUM and VERB. The following categories
cannot be inflected: ADV, DET, ART, UTT-INT, CONJ, PREV, ONO, PUNCT and PREP.
For postpositions see Section \ref{postp}.

\begin{table}[h]
\begin{center}
\begin{tabular}{|l|l|}
\hline
Tag & POS category \\
\hline
ADJ & adjective \\
ADV & adverb \\
ART & article \\
CONJ & conjunction \\
DET & determiner \\
NOUN & noun \\
NUM & numeral \\
ONO & onomatopoeic \\
POSTP & postposition \\
PREP & preposition \\
PREV & preverb \\
PUNCT & punctuation \\
UTT-INT & utterance/interjection \\
VERB & verb \\
% & \\
\hline
\end{tabular}
\end{center}
\caption{POS categories of HunMorph}
\label{pos_list}
\end{table}

\section{Encoding inflectional information of nouns and nominal
categories}

An actual feature set was designed following the above considerations for
the morphological analysis of Hungarian. 

In the case of a noun four binary features have to be
specified. They are $\pm PLUR $ (number), $\pm POSS$ (possessor), $\pm ANP$
(possessed) and $\pm CASE$\footnote{There are two more morphosyntactic
features that are in fact part of this tree. These are $\pm PERS $ 
and $\pm POSTP $, which are discussed in sections \ref{pronouns} and
\ref{postp} respectively.}. All of these can be continued as specified in
Figure 
%\ref{noun_tree} 
% vmiért ez a szám nemjó
1.~and in Table \ref{noun_infl}. Adjectives and numerals
can take the same set of inflections as nouns.

The following restrictions apply to the combination of the features:

\begin{itemize}
\item the $\pm CASE$ feature has to be continued by one of 16 cases,
\item the $\pm PLUR $, $\pm POSS$ and $\pm ANP$ features can be contitued or
can appear on their own,
\item the features $ \pm 1$ and $ \pm 2$ exclude each other,
\item if the $\pm PLUR $ feature of $\pm POSS$ is positive, then the $\pm
FAM$ feature cannot be positive,
\item if the $\pm PLUR $ and the $\pm POSS$ feature are positive
simultaneously, then the $\pm FAM$ feature cannot be positive.

\end{itemize}

\begin{figure}

\Tree [.NOUN  [.PLUR  FAM  ]  [.POSS 1 2 PLUR ]  [.ANP PLUR ] [.CAS ACC
DAT INS  ... ] ]

\caption{ The signature of the graphs originating from the root node
$NOUN $ }
\end{figure}
\label{noun_tree}

The morphosyntactic annotation of an inflected word-form is represented by
a sub-tree of the above tree. The paths originate from the root and they
encode the positive values of the attribute-value matrix. The
negative values of the signature are not present in the tree.
The tree is thus equivalent to an AVS encoding the inflectional
properties of a word-form, however, it is free of redundancy and can
be easily linearized by bracketing the nodes of the tree. 

\begin{table}[h]
\begin{center}
\begin{tabular}{|l|l|l|l|l}
\hline

number:	& singular & ({\em sógor}) & \verb#<-PLUR># \\

 & plural & & \\
 & & ,,simple" ({\em sógor-ok}) & \verb#<+PLUR<-FAM>># \\
 & & familiáris birtokos ({\em sógor-ék}) & \verb#<+PLUR<+FAM>># \\

\hline

possessor: & none & & \verb#<-POSS>#\\
 & overt possessor & & \\
 & & person: & \\
 & & 1st ({\em sógor-om}) & \verb#<+POSS<+1><-2>># \\
 & & 2nd ({\em sógor-od}) & \verb#<+POSS<-1><+2>># \\
 & & 3rd ({\em sógor-a}) & \verb#<+POSS<-1><-2>># \\

 & & number: & \\
 & & singular ({\em sógor-ai}) & \verb#<+POSS<-PLUR>># \\
 & & plural ({\em sógor-uk}) & \verb#<+POSS<+PLUR>># \\

\hline

possessed: & none & & \verb#<-ANP># \\
 & overt possessed & number & \\
 & & singular ({\em sógor-é}) & \verb#<+ANP<-PLUR>># \\
 & & plural ({\em sógor-éi}) & \verb#<+ANP<+PLUR>># \\ 

\hline
case: & ,,none'' & NOM ( {\em sógor}) & \verb#<-CAS># \\

 & overt, one of 16 cases: & ACC ( {\em sógort})& \verb#<+CAS<+ACC>># \\
 & & DAT ({\em sógor-nak}) & \verb#<+CAS<+DAT>># \\
 & & INS ({\em sógor-ral}) & \verb#<+CAS<+INS>># \\
 & & CAU ({\em sógor-ért}) & \verb#<+CAS<+CAU>># \\
 & & TRA ({\em sógor-rá}) & \verb#<+CAS<+TRA>># \\
 & & SUE ({\em sógor-on}) & \verb#<+CAS<+SUE>># \\
 & & SBL ({\em sógor-ra}) & \verb#<+CAS<+SBL>># \\
 & & DEL ({\em sógor-ról}) & \verb#<+CAS<+DEL>># \\
 & & INE ({\em sógor-ban}) & \verb#<+CAS<+INE>># \\
 & & ELA ({\em sógor-ból}) & \verb#<+CAS<+EAL>># \\
 & & ILL ({\em sógor-ba}) & \verb#<+CAS<+ILL>># \\
 & & ADE ({\em sógor-nál}) & \verb#<+CAS<+ADE>># \\
 & & ALL ({\em sógor-hoz}) & \verb#<+CAS<+ALL>># \\
 & & ABL ({\em sógor-tól}) & \verb#<+CAS<+ABL>># \\
 & & TER ({\em sógor-ig}) & \verb#<+CAS<+TER>># \\
 & & FOR ({\em sógor-ként}) & \verb#<+CAS<+FOR>># \\
\hline

\end{tabular}
\end{center}
\label{noun_infl}
\caption{Inflectional features of nouns}
\end{table}



We present some examples with their full inflectional specification as an
AVS and the linearization of their (sub)tree as it appears in the analysis
where the outermost brackets and the \verb|+| signs are omitted and the POS
category is preceded by a slash and the lemma of the word-form.
%Az alábbi példák a szóalak teljes inflexiós specifikációját mutatják
%jegy--érték-struktúrával, valamint a linearizált fagráfos kódolással.


%\begin{tabular}{ll}

%\begin{enumerate}%[a.]
\begin{tabbing}
abit\=\kill
{\it kutya} 'dog' \\
 \> \verb|<NOUN<-PLUR><-POSS><-ANP><-CAS>>|\\
 \> \verb|kutya/NOUN| \\
\textit{kutyának} 'for/to the dog' \\
 \> \verb|<NOUN<-PLUR><-POSS><-ANP><+CAS<+DAT>>>| \\
 \> \verb|kutya/NOUN<CAS<DAT>>| \\
{\it kutyáink} 'our dogs' \\
\> \verb|<NOUN<+PLUR<-FAM>><+POSS<+1><-2><+PLUR>><-ANP><-CAS>>|\\
\> \verb|kutya/NOUN<PLUR><POSS<1><PLUR>>| \\
{\it kutyáéi} 'those things of the dog' \\
\> \verb|<NOUN<-PLUR><-POSS><+ANP<+PLUR>><-CAS>>|\\
\> \verb|kutya/NOUN<ANP<PLUR>>|\\
{\it kutyáikéit} 'those things of their dogs.{\sc ACC}' \\
\>
\verb|<NOUN<+PLUR<-FAM>><+POSS<-1><-2><+PLUR>><+ANP<+PLUR>><+CAS<+ACC>>>|
\\
\> \verb|kutya/NOUN<PLUR><POSS<PLUR>><ANP<PLUR>><CAS<ACC>>|\\
\end{tabbing}


\section{Encoding inflectional information for verbs}

A maximal verbal word-form has to have several properties specified. The
properties are specified in Figure 
%\ref{verb_tree}.
2.\footnote{The tree has been
cut into two parts for reasons of clarity.} and in Table
\ref{verb_infl}. The following restrictions apply to the combination of the
features:

\begin{itemize}
\item only one of $ \pm SUBJUNC $ and $ \pm COND $ can be positive
simultaneously,
\item the feature $ \pm PAST $ can only be positive if both $ \pm SUBJUNC $
and $ \pm COND $ are negative,
\item if the feature $ \pm OBJ $ is positive than its daughter feature has to
positive as well,
\item the feature $ \pm INF $ can only combine with the feature $ \pm PERSON
$ $ \pm PLUR$ and $ \pm MODAL $.
\end{itemize}

\begin{table}[htdp]
\begin{center}
\begin{tabular}{|l|l|l|l|l}
\hline
modality: & none & & \verb#< -MODAL># \\
 & & modal ({\em futhat}) & \verb#< +MODAL># \\
\hline
mood: & conjunctive & & \verb#<-SUBJUNC><-COND># \\
 & & subjunctive/imperative & \\
 & & (no tense) & \verb#< +SUBJUNC># \\
 & & conditional & \verb#<+COND># \\
\hline
tense: & present & & \verb#<-PAST><-FUT>#\\
 & past \footnotemark & & \verb#<+PAST># \\
 & future & & \\
 & (only for the copula '\textit{van}') & & \verb#<+FUT># \\
\hline
number/person: & subject person & & \\
 & & 1st ({\em futok}) & \verb#<+PERS<+1><-2>># \\
 & & 1st ({\em várlak}) & \\
 & & with 2nd person object & \verb#<+PERS<+1<+OBJ<+2><-2>># \\
 & & 2nd ({\em futsz}) & \verb#<+PERS<-1><+2>># \\
 & & 3rd ({\em fut}) & \verb#<+PERS<-1><-2>># \\
 & subject number & & \\
 & & singular ({\em fut}) & \verb#<-PLUR># \\
 & & plural ({\em futnak}) & \verb#<+PLUR># \\
\hline
 definiteness & indefinite & ( {\em lát}) & \verb#<-DEF># \\
 & definite & ( {\em látja}) & \verb#<+DEF># \\
\hline
\end{tabular}
\footnotetext{not a single word-form in conditional}
\end{center}
\label{verb_infl}
\caption{Inflectional features of verbs}
\end{table}

\begin{figure}[hb]

\Tree [.VERB  MODAL SUBJUNC COND PAST INF ]

%\end{figure}
%\label{verb_tree}
%\begin{figure}

\Tree [.VERB  PLUR [.PERS  [.1 [.OBJ 2 ] ] 2  ] DEF ]

\vspace{.5cm}

%\caption{ The signature of the graphs originating from the root node
%\texttt{VERB} (contd.)}
\caption{ The signature of the graphs originating from the root node
$VERB $}
\end{figure}
\label{verb_tree}

% no PAST if COND or SUBJUNC
% OBJ 2 only together
% 
The annotation of verbs with inflectional suffixes is similar to that of
nouns. Examples are:
%Az igei infelexióval ellátott alakok kimeneti kódja hasonló a
%fõnéviekhez. Két példa a teljes és egyszerûsített kódra:

\begin{tabbing}
abit\=\kill
%{\it kutya} \\
% \> \verb|<+NOUN<-PLUR><-POSS><-ANP><-CAS>>|\\
% \> \verb|<NOUN>| \\
{\em lát} 'he sees' \\
 \> \verb|<VERB<-INF><-MODAL><-PAST><-COND><-SUBJ-IMP><-PERS><-PLUR><-DEF>>|
\\
 \> \verb|lát/VERB| \\
{\em láttál} 'you saw' \\
 \>
\verb|<VERB<-INF><-MODAL><+PAST><-COND><-SUBJ-IMP><+PERS<+2>><-PLUR><-DEF>>|
\\
 \> \verb|lát/VERB<PAST><PERS<2>>| \\
%\item
 {\em láthassátok} 'that you may see it' \\
 \>
\verb|<VERB<-INF><+MODAL><-PAST><-COND><+SUBJ-IMP><+PERS<+2>><+PLUR><+DEF>>|
\\ 
 \> \verb|lát/VERB<MODAL><SUBJUNC><PERS<2>><PLUR><DEF>| \\
\end{tabbing}

\section{Derivation and compunding}

\subsection{Representing derivational information}

The above tree structure is not directly suited to decribe derivation.
However, a derivational suffix can be treated as a relation between two
lexical entries. This way we can extend the tree structure by representing
derivation as a directed edge between nodes of inflectional categories
(roots of trees). Derivation can change or leave intact the POS category of
a word. The POS category of the resulting word is the output category of
the last derivational suffix, and the derivated word can undergo further
inflectional suffixing. Inflected forms, however, cannot be subjected to
derivation. Consider the following examples:

\begin{tabbing}
faxolások \=  <[fax]NOUN[l]VERB[gAt]VERB[Ás]NOUN> \= faxing \kill
{\em fax}   \>   \verb+fax/NOUN+ \> 'fax'\\
{\em faxol} \>    \verb+fax/NOUN[ACT]/VERB+ \> 'to send a fax' \\
{\em faxolás} \>   \verb+fax/NOUN[ACT]VERB[GERUND]/NOUN+ \>
'faxing' \\
\end{tabbing}


%Az eddigi megfontolásokból automatikusan adódik, hogy sem az
%inflektált alakok, sem a részben specifikált (azaz nem gyökér)
%``tantumok'' nem vethetõk alá képzésnek.
%% hogy ez következik-e? 

\subsection{Annotation of compounds}

Compounding is encoded in the annotation by use of a \verb|+| sign. A preverb
followed by a verb is treated as a compound in this respect, as well as a
$NOUN$\verb|+|$NOUN$ or an $ADJ$\verb|+|$NOUN$ compound. Compounding is
similar to derivation in
that only the last part of the word can be subjected to inflectional
suffixing and that the output category of the compound is determined by the
last component. E.g.: 

\begin{tabbing}
abit\=\kill
\textit{rákkoktél} 'shrimp coctail' \\
 \> \verb|rák/NOUN+koktél/NOUN|  \\
\textit{keresztüllövi} 'he shoots it through' \\
 \> \verb|keresztül/PREV+lõ/VERB<DEF>| \\
\end{tabbing}

\section{Pronouns and postpositions}

\subsection{Pronouns} \label{pronouns}


In Hungarian a pronoun can substitute for any noun, adjective or numeral,
as well as for adverbs. The inflection of pronouns, where applicable,
conforms to the restrictions imposed by the inflectional features
and the tree-structure discussed above. This enables us to avoid the use of
'pronoun' as a POS category, and use instead the category which the pronouns
stand for.

Personal pronouns are nouns, but they are subject to the following
restrictions: their $POSS$ feature must be negative and their 
$ PERS $ feature has to be specified. Otherwise, the $ PERS $
feature can combine with any other features ($ PLUR$, $ANP$, $CAS$). E.g.:

\begin{tabbing}
abit\=\kill
{\it ti} 'you.{\sc PL}' \\
 \> \verb|ti/NOUN<PERS<2>><PLUR>|\\
{\it titeket} 'you.{\sc PL}.{\sc ACC}' \\
 \> \verb|ti/NOUN<PERS<2>><PLUR><CAS<ACC>>|\\
\end{tabbing}

Possessive pronouns are personal pronouns with a possessed feature, thus they
carry the \verb+ANP+ feature as well. Examples include:

\begin{tabbing}
abit\=\kill
{\it tiétek} 'yours' \\
 \> \verb|ti/NOUN<PERS<2>><PLUR><ANP>| \\
{\it tieteknek} 'to/for yours' \\
 \> \verb|ti/NOUN<PERS<2>><PLUR><ANP><CAS<DAT>>| \\
\end{tabbing}

The anaphoric possessive can be repeated as shown in the next example:
\begin{tabbing}
abit\=\kill
{\it enyémé} 'that of my something' \\
 \> \verb|én/NOUN<PERS<1>><ANP<ANP>>| \\
\end{tabbing}

The above properties are shared by other pronouns including demonstrative,
reflexive, relative, interrogative pronouns. The inflection of adjectival
and numeral pronouns resemble to that of adjectives and numerals
respectively, i.e. they are tagged as \verb|ADJ| and \verb|NUM| and take the
usual inflections.

\subsection{Postpositions} \label{postp}

The function of postpositions is the same as that of case-suffixes, although
some differences have to be noted. One major difference is that postpositions
are separate words and, as such, have their own annotation. Furthermore, a
number of postpositions can take the $PERS $ feature and as their syntactic
distribution (function) is the same as that of personal pronouns, these 
inflected postpositons will be annotated as nouns. In this case the
$POSTP$ feature of the tree also takes the positive value and the name of
the relevant postposition has to be specified in the annotation as
well\footnote{The full list of tags that can be dominated by a $POSTP$ tag can
be seen in Table \ref{postp_list}.}:

\begin{tabbing}
abit\=\kill
\textit{mellettetek} 'next to you.{\sc PL}' \\
 \> \verb|ti/NOUN<POSTP<MELLETT>><PERS<2>><PLUR>| \\
\end{tabbing}

If the  $POSTP$ feature is positive, the $CAS$, $ANP$ and $FAM$ features have
to be negative. Uninflected postpositions have the characteristics of a main
POS category in that they can, for example, undergo derivation. Examples
are:

\begin{tabbing}
abit\=\kill
mellett 'next to' \\
 \> \verb|mellett/POSTP| \\
mellettetek next to you.{\sc PL} \\
 \> \verb|ti/NOUN<POSTP<MELLETT>><PERS<2>><PLUR>| \\
mellettiekben 'in those that are next to' \\
 \> \verb|mellett/POSTP[ATTRIB]/ADJ<PLUR><CAS<INE>>| \\
\end{tabbing}

\begin{table}[htdp]
\begin{center}
\begin{tabular}{ll}
ALÁ & (to) under X 	 \\
ALATT & under X 	 \\
ALÓL & from under X 	 \\
ÁLTAL & by X, by way of X 	 \\
ELÉ & before X, in front of X 	 \\
ELÉB & before X, in front of X (archaic) \\
ELLEN & against X 	 \\
ELLEN & contrary to X 	 \\
ELÕL & from (in front of) X 	 \\
ELÕTT & before X, in front of X 	 \\
FELÉ & towards X 	 \\
FELETT & above X, over X 	 \\
FELÕL & from (the direction of) X, as for X 	 \\
FELÜL & from (above/over) X 	 \\
FÖLÉ & above X, over X 	 \\
FÖLIBE & above X, over X (archaic) \\
FÖLÖTT & above X, over X 	 \\
FÖLÜL & from (above/over) X 	 \\
HELYETT & instead of X 	 \\
IRÁNT & person marking with infixing \\
KÖRÉ & (to) around X 	 \\
KÖRÖTT & around X 	 \\
KÖRÜL & around X 	 \\
KÖRÜLÖTT & around X 	 \\
KÖZÉ & to (between many, among many) X 	 \\
KÖZIBÉ & to (between many, among many) (archaic) \\
KÖZÖTT & between X, among X 	 \\
KÖZT & between X, among X 	 \\
KÖZÜL & out of X, from among X 	 \\
LÉT & these can have inflected demostrative forms \\
MELLÉ & to somewhere near X 	 \\
MELLETT & beside X, by X, (somewhere) near X 	 \\
MELLÕL & from somewhere near X 	 \\
MIATT & because of X 	 \\
MÖGÉ & (to) behind X 	 \\
MÖGÖTT & behind X 	 \\
MÖGÜL & from (behind) X 	 \\
NÉLKÜL & without X 	 \\
RÉSZ & as concerns X 	 \\
RÉSZ & for X 	 \\
SZÁM & for X (recipient) 	 \\
SZERINT & according to X 	 \\
UTÁN & after X 	 \\

\end{tabular}
\end{center}
\label{postp_list}
\caption{List of features that can combine with the feature $ PERS$ }
\end{table}

\section{Derivational morphemes} \label{derivmorpheme}

The full list of derivational morphemes can be seen in Table
\ref{deriv_all}. The output tag is followed by an (approximate) English name
of the suffix and an allomorph. The input and output categories of the suffix
are also indicated.

%\thispagestyle{empty}
% ahova a tablazat kerul, oda nem kene oldalszam. nemtom hogy kell
\begin{table}[h]
\caption{Derivational morphemes}
\begin{center}
\begin{tabular}{|l|l|l|l|}
\hline
Tag & explanation & example & POS \\
\hline \hline
FREQ & frequentative & gat  & VERB $\rightarrow$ VERB \\
MEDIAL & medial & ódik  & VERB $\rightarrow$ VERB \\
CAUS & causative & tat  & VERB $\rightarrow$ VERB \\
PART & adverbial participle & va  & VERB $\rightarrow$ ADV \\
PERF\_PART & perfect adverbial participle & ván  & VERB $\rightarrow$ ADV \\
IMPERF\_PART & imperfect adjectival participle & ó  & VERB $\rightarrow$ ADJ
\\
FUT\_PART & future adjectival participle & andó  & VERB $\rightarrow$ ADJ \\
PERF\_PART & perfect adjectival participle & ott  & VERB $\rightarrow$ ADJ \\
NEG\_PERF\_PART & negative perfect adjectival participle & atlan  & VERB
$\rightarrow$ ADJ \\
GERUND & gerund & ás  & VERB $\rightarrow$ NOUN \\
NEG\_MODAL\_PART & negative modal adjectival participle & hatatlan  & VERB
$\rightarrow$ ADJ \\
MODAL\_PART & modal adjectival participle & ható  & VERB $\rightarrow$ ADJ \\
\hline 
REG\_ACT & regular activity & kodik  & NOUN $\rightarrow$ VERB \\
ABSTRACT & abstract & ság  & NOUN $\rightarrow$ NOUN \\
MRS & mrs & né  & NOUN $\rightarrow$ NOUN \\
DIMIN & diminutive & ka  & NOUN $\rightarrow$ NOUN \\
%DIGIT & digit & ? & ? \\
ATTRIB & attributive & s  & NOUN $\rightarrow$ ADJ \\
MET\_ATTRIB & metonymical attributive & i  & NOUN $\rightarrow$ ADJ \\
INAL\_ATTRIB & inalienable attributive & jú  & NOUN $\rightarrow$ ADJ \\
NEG\_ATTRIB & negative attributive & talan  & NOUN $\rightarrow$ ADJ \\
TYPE1 & type1 & szeru  & NOUN $\rightarrow$ ADJ \\
TYPE2 & type2 & féle  & NOUN $\rightarrow$ ADJ \\
TYPE3 & type3 & nemu  & NOUN $\rightarrow$ ADJ \\
TYPE\_RANK & type rank & rangú  & NOUN $\rightarrow$ ADJ \\
NEG\_ATTRIB2 & negative attributive2 & mentes  & NOUN $\rightarrow$ ADJ \\
TYPE4 & type4 & fajta  & NOUN $\rightarrow$ ADJ \\
LOC\_INE & locative inessive & beli  & NOUN $\rightarrow$ ADJ \\
QUANTITY & quantity & nyi  & NOUN $\rightarrow$ NUM \\
ESS\_FOR & essivus formalis & képpen  & NOUN $\rightarrow$ ADV \\
COM & comitative & stul  & NOUN $\rightarrow$ ADV \\
PERIOD1 & period1 & anként  & NOUN $\rightarrow$ ADV \\
PERIOD2 & period2 & onta  & NOUN $\rightarrow$ ADV \\
ACT & activity & oz  & NOUN $\rightarrow$ VERB \\
ACT2 & activity2 & ol  & NOUN $\rightarrow$ VERB \\
\hline 
COMPAR & comparative & bb  & ADJ $\rightarrow$ ADJ \\
SUPERLAT & superlative & leg-bb & ADJ  $\rightarrow$ ADJ \\
SUPERSUPERLAT & supersuperlative & legesleg-bb  & ADJ  $\rightarrow$ ADJ \\
COMPAR\_DESIGN & comparative designative & bbik & ADJ  $\rightarrow$ ADJ \\
SUPERLAT\_DESIGN & superlative designative & leg-bbik & ADJ  $\rightarrow$ ADJ
\\
SUPERSUPERLAT\_DESIGN & supersuperlative designative & legesleg-bbik  & ADJ 
$\rightarrow$ ADJ \\
MANNER & manner & lag  & ADJ $\rightarrow$ ADV \\
MANNER & manner & an  & ADJ $\rightarrow$ ADV \\
INTRANS\_RESULT & intransitive resultative & odik/ul  & ADJ $\rightarrow$ VERB
\\
TRANS\_RESULT & transitive resultative & ít  & ADJ $\rightarrow$ VERB \\
\hline
MULTIPL-ITER & multiplicative iterative & szor  & NUM $\rightarrow$ ADV \\
MULTIPL-ITER & multiplicative iterative & szoroz  & NUM $\rightarrow$ VERB \\
ITER\_ATTRIB & iterative attributive & szori  & NUM $\rightarrow$ ADJ \\
MULTIPL\_ATTRIB & multiplicative attributive & szoros  & NUM $\rightarrow$ ADJ
\\
MULTIPL & multiplicative & szorta  & NUM $\rightarrow$ ADV \\
AGGREG & aggregative & an  & NUM $\rightarrow$ ADV \\
FRACT & fractional & ad  & NUM $\rightarrow$ NUM \\
ORD & ordinal & odik  & NUM $\rightarrow$ NUM \\
DATE & date & odika  & NUM $\rightarrow$ NOUN \\
\hline
ATTRIB & attributive & i & POSTP $\rightarrow$ ADJ\\
\hline
\end{tabular}
\end{center}
\label{deriv_all}
\end{table}

\section{Comparison with other systems}

The annotation system described in this document is independent of the
implementation and the technical details of the morphological analysis. As
such it is especially suitable to act as a common ground when comparing
different formalisms. 

While designng our system we examined the MSD coding system\cite{erjavec1997},
which is positional, i.e. it has fixed positions for each morphosyntactic
property and these positions can be either filled in or left empty. An MSD
code is not suited to describe derivations, it deals only with inflectional
suffixing. The mapping between the two systems is ambiguous, but we designed
our annotation system in a way that it should contain at least as much
information as the MSD system.

\bibliographystyle{plain}
\bibliography{all_bib,our_publications}

\end{document}
